---
title: "Assignment 2"
format:
  html:
    embed-resources: true
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo       = TRUE, 
                      fig.height = 3, 
                      fig.width  = 6,
                      fig.align  = "center")
ggplot2::theme_set(ggplot2::theme_bw())

```

```{r}
library(tidyverse)
#Question 1
college_data <- read_csv("../Data_413/homework_2/collegedata.csv")
```

```{r}
#Question 2
nrow(college_data)
ncol(college_data)
```

```{r}
#Question 3
college_data %>%
  select(INSTNM, SAT_AVG, ADM_RATE)
```

```{r}
#Question 4
drop_na(college_data)
college_data %>%
  ggplot(aes(x=SAT_AVG, y=ADM_RATE))+
  labs(x="SAT Average", y="Admission Rate")+
  geom_point(color="blue")
```

## Instructions

Complete the following exercises **using only the tidyverse packages** (e.g., `dplyr`, `tidyr`, `ggplot2`, `readr`, `stringr`, `forcats`, `lubridate`, `purrr`, etc.)

**Important:** This assignment is intended to assess your proficiency with the **tidyverse**. Solutions that use **base R** or **packages outside the tidyverse** to solve the problems will **not receive credit** unless explicitly permitted in the question.

1.  Load the necessary **tidyverse** libraries.
2.  Answer each question in a separate R code chunk.
3.  Provide a detailed explanation of your approach for each solution.
4.  Render your R Markdown document to an HTML file.
5.  Submit the rendered HTML file to Canvas.

# Question:

- Task 1: Read data using a relative path
  - I set the working directory to my documents folder, and then my data was my homework_2 folder within my data_413 folder so I had to go down my folders in order to get to it

``` r
Example:
college_data <- read_csv("../data/collegedata.csv")
```

- Task 2:Determine rows and columns

  - I printed the number of rows and columns inside of the data set using nrow and ncol

- Task 3: Use tidyverse to select INSTNM, SAT_AVG, and ADM_RATE

  - Use a pipe and the select function to select the three categories

- Task 4: Create a scatter plot for SAT_AVG and ADM_RATE (Remove NA)

  - Used ggplot to create a scatter plot of the two data points and removed NA

## Submission

- After completing **each question**, save your Quarto file, render it, then **stage and commit** your changes.

- Each commit should:

  - Represent **one logical change**.
  - Have a **short, descriptive** commit message.
  - Be written in the **present tense** (imperative mood).

  **Examples:**

  **Bad:** `Fix bug in the project` *Too vague—it does not explain which bug was fixed.*

  **Bad:** `Fixed crash on login screen when password is empty` *Uses the past tense.*

  **Good:** `Fix crash on login screen when password is empty`

- Include well-commented code and clear explanations for each solution.

- Make **at least one meaningful commit per question/part** (a minimum of **4 meaningful commits**).

- **Push your work to your** GitHub\*\*. ane post the link on the text bar of the Canvas assignment.

- Assignments that are **not pushed to GitHub** will receive **no more than 60% of the available points**.

- Submit the rendered HTML file to **Canvas**. Assignments that are **not submitted to Canvas** will also receive **no more than 60% of the available points**.

- If you forget to submit your work to **GitHub** or **Canvas**, you have **up to three (3) days** after the due date to correct the submission. A **10% late penalty** will be applied to the assignment. **After three days, no submissions or corrections will be accepted.**

- **No corrections, re-submissions, or missing submissions will be accepted after the assignment has been graded**, including forgotten GitHub or Canvas submissions.

**Good luck!**
